\section*{The Lost Tomb of Amaar}

\begin{center}
    \scalebox{0.5}{
        \begin{tikzpicture}
            % Rooms
            \roomSquare{1}{0}{5}
            \roomCircle{0}{7}{7}{red}
            \roomCircle{1}{14}{5}{gray!20}
            \roomCircle{1}{24}{5}{white}
            \roomCircle{0}{29}{7}{white}

            % Hallways
            \roomRectangular{3}{5}{1}{2}{white}
            \roomRectangular{2}{19}{3}{5}{white}

            % Misc
            \roomRectangular{2}{7}{3}{1}{gray}
            \roomRectangular{2}{13}{3}{1}{gray}
            \pillar{1}{ 9}
            \pillar{6}{10}
            \pillar{4}{ 8}
            \pillar{5}{12}
            \pillar{3}{10}
            \pillar{1}{12}
            \pillar{2}{11}

            % Annotations
            \annotaton{3}{  2}{1}
            \annotaton{3}{5.5}{2}
            \annotaton{3}{ 10}{3}
            \annotaton{3}{ 16}{4}
            \annotaton{3}{ 21}{5}
            \annotaton{3}{ 26}{6}
            \annotaton{3}{ 34}{8}

            % Doors
            \doorClosed{3}{0}
            \doorClosed{3}{5}
            \doorClosed{3}{7}
            \doorClosed{3}{14}
            \doorClosed{3}{19}
            \doorClosed{3}{24}
            \doorClosed{3}{29}
            
            % Grid
            \mapGrid{7}{36}
        \end{tikzpicture}
    }
\end{center}

\subsection*{1}
\subsubsection*{Death}
\begin{itemize}
    \item 
\end{itemize}
\subsubsection*{Peace}
\begin{itemize}
    \item A blanket, rolled up
    \item A chair
    \item A small chest
\end{itemize}
\subsubsection*{War}
\begin{itemize}
    \item A Sword
    \item A piece of armor
    \item 
\end{itemize}
\subsubsection*{Destruction}
\begin{itemize}
    \item A piece of obsidian
    \item A skull
\end{itemize}

\amaar{king}{hope}{
Welcome. I now sing my-people-song. I have seen peace war destruction and death. I am at peace despite my-people-death, they found the world trotter in the end. Understanding their-struggle brings escape, my task is find the world trotter too. Bring what represents-world trotter here
}{
Welcome. I now sing my-people-song. I have seen peace war destruction and death. I am at peace despite my-people-death, they found the world trotter in the end. Understanding their-struggle brings escape, my task is find the world trotter too. Bring what represents-world trotter here
}{0.25}{4}

\subsection*{Room 8 - Death}
\amaar{death}{knowledge}{
Death text 1
}{
Death text 1
}{0.25}{4}

Death is the ending of life but the beginning of the next.

\subsection*{Room 6 - Peace}
This room is

\amaar{agony}{peace}{
I won her heart above all others,\\
We have no problems no risk no bothers.\\
The perfect marriage for all to show,\\
It is these days that kills me slow.\\

The corn stands solumn in the field,\\
This summer will bring decent yeild.\\
Not much to do after we sow,\\
It is these days that kills me slow.\\

The competition at perfect speed,\\
Not much to fight for or compeed.\\
The land is peacefull with quiet flow,\\
It is these days that kills me slow.\\

The scholars mill around the place,\\
The halls so quiet full of space.\\
Young folks laugh from rooms below,\\
It is these days that kills me slow.\\
}{
I won -her heart above all others,
me-people have no problems no risk no bothers.
The perfect marriage for all to show,
It is these days that kills me slow.

The corn stands solumn in the field,
This summer will bring decent yeild.
Not much to do after we sow,
It is these days that kills me slow.

The competition at perfect speed,
Not much to fight for or compeed.
The land is peacefull with quiet flow,
It is these days that kills me slow.

The scholars mill around the place,
The halls so quiet full of space.
Young folks laugh from rooms below,
It is these days that kills me slow.
}{0.25}{4}

\amaar{king}{peace}{
The King once announced a prize to the artist who would paint the best painting depicting the world trotter. Many great painters sent you several of their best art pieces. One of the pictures was by many declared the perfect picture. It was of a calm lake perfectly mirroring a peacefully towering snow-capped mountains. Overheard was a blue clear sky with fluffy clouds.

However, you did not agree, you found the perfect picture instead. In it, the sky looked very angry, there were lightning. This did not look peaceful at all. It looked like the artist has mistakenly submitted his painting depicting storm. However,  closely at the painting, and saw a tiny bush growing in the cracks in the rock. In the bush a mother bird had built her nest. In the midst of the rush of angry weather, the bird sat on her nest with peace. You declared this picture the winner. To the tune of peace.
}{
The King once announced a prize to the artist who would paint the best painting depicting the world trotter. Many great painters sent you several of their best art pieces. One of the pictures was by many declared the perfect picture. It was of a calm lake perfectly mirroring a peacefully towering snow-capped mountains. Overheard was a blue clear sky with fluffy clouds.

However, you did not agree, you found the perfect picture instead. In it, the sky looked very angry, there were lightning. This did not look peaceful at all. It looked like the artist has mistakenly submitted his painting depicting storm. However,  closely at the painting, and saw a tiny bush growing in the cracks in the rock. In the bush a mother bird had built her nest. In the midst of the rush of angry weather, the bird sat on her nest with peace. You declared this picture the winner. To the tune of peace.
}{0.25}{4}


\subsection*{Room 4 - War}
The floor is made of practical symmetrical stones. The walls are simple but sturdy and the cieling is nonassuming but high. In each corner stands is an armorstand holding black dull armor.

\subsubsection*{Story 1}
The story about the ship and the  

\subsection*{Room 3 - Destruction}
When entering you are hit by a wall of heat. You realize how nice and cool the previous room had been and you start feel the sweat dripping from your forehead. You enter on a platou overlooking a hellish landscape. A few meters down you see .

The walls are lined with 

In destruction lies ultimate death. Death is normally only applied to living things, i guess by definition. However, i argue that death can be applied to inanimate objects too. We assume the nature of objects given by the fade. Their existence as objects are given by our recognition of their essence. Lets take the chair, it is not necessary defined by its . Destruction, by definition, removes this essence from the object. It is possible to restore the object to its essence, however this will always require energy, which in turn always requires destruction of other material. Assuming the scriptures of Iholyn we assume the terminal nature of all items. This makes the world finite and all entropian movement shorten .

The last gift to you before a grandads death
Two 