\section*{The Third Eye}

\subsection*{Alternative Names}
The Fade, \enquote{Mellemplanet}, \enquote{Ideernes Plan}

\subsection*{Description}
This place is inhabited by creatures of pure mind and soul. Their reality exists purely as a product of their own creation. This is both what makes them incredibly powerful and limit their powers. They have the power to affect any other plane, but only through the mind and soul of the creatures that inhabit them. Creatures of other planes often travel to this plane to trade items, as anything you are certain you own in this plane have a tendency to manifest in the planes you travel to and live in. Many creatures find the concept of time useless and only travel (like we slowly travel forward in time) to accomendate the creatures visiting them. This often have, to creature from other planes, an odd effect on how they approach topics.

\subsubsection*{How to get there}
Since Mystra destroyed Conjuration interplanar travel is impossible in the form given to you in your own plane. However, this plane is a bit of a loophole. Since this plane exists purely on the basis of observation it is possible to travel here if you become aware of it and certain of its existence and your ability to travel here. This is far easier said than done and only creatures who are in perfect spiritual balance and have a deep understanding of their own mind and soul can observe this realm. Only a few creatures the material plane have managed to travel to this place and interract with its beings in the Era of Heroes.